A Formalization of Typed Lua

### 2015-08-21 doc/papers/dls15/paper.tex
add country to affiliation

\authorinfo{André Murbach Maidl}
           {PUC-Rio}
           {amaidl@inf.puc-rio.br}
\authorinfo{Fabio Mascarenhas}
           {UFRJ}
           {mascarenhas@acm.org}
\authorinfo{Roberto Ierusalimschy}
           {PUC-Rio}
           {roberto@inf.puc-rio.br}

>>>>

\authorinfo{André Murbach Maidl}
           {PUC-Rio, Brazil}
           {amaidl@inf.puc-rio.br}
\authorinfo{Fabio Mascarenhas}
           {UFRJ, Brazil}
           {mascarenhas@acm.org}
\authorinfo{Roberto Ierusalimschy}
           {PUC-Rio, Brazil}
           {roberto@inf.puc-rio.br}
